---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# rmiscfun

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/gbasulto/rmiscfun.svg?branch=master)](https://travis-ci.org/gbasulto/rmiscfun)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/gbasulto/rmiscfun?branch=master&svg=true)](https://ci.appveyor.com/project/gbasulto/rmiscfun)
[![Codecov test coverage](https://codecov.io/gh/gbasulto/rmiscfun/branch/master/graph/badge.svg)](https://codecov.io/gh/gbasulto/rmiscfun?branch=master)
<!-- badges: end -->


The goal of rmiscfun is provide call functions that I use in different projects (at work and personal ones.)


## Prerequisites


1. Install [Rtools](https://cran.r-project.org/bin/windows/Rtools/) (Only if you are on Windows): Download and execute the recommended EXE file in [this link](https://cran.r-project.org/bin/windows/Rtools/).
1. Install `devtools` package in `R`:
``` r
install.packages("devtools")
```
1. Install `tidyverse` package in `R`. I use functions from several tidyverse packages, so it is better to have them all installed.
``` r
install.packages("tidyverse")
```

## Installation

You can install the current version of rmiscfun from [GitHub](https://github.com/) with:

``` r
devtools::install_github("gbasulto/rmiscfun")
```

## Available Functions

| Function | Brief description |
| :-------------------- | :------------------------------------------------------------|
| `glance_data`         | Summarize both, categorical and numerical variables in a dataframe |
| `glance_data_in_workbook` | Similar to `glance_data`, but it breaks the summary into types and allows the used to save it in an Excel Workbook |
| `plot_numerical_vars` | Graphical summaries of numerical variables using functions from `ggplot2` and `GGally`|
| `clean_colnames` | Clean column names |
| `clean_col_content` | Clean column content if a variable is character or factor |

## Examples

I am using the Iris dataset in R, which has 5 variables. The first four are measurements 150 flores and the last column specifies the species (there are 50 flowers of each species).

```{r iris}
## Uncomment the following line to read the documentation of the dataset.
## help(iris)

head(iris)
```

#### `glance_data`


```{r glance_data, eval = FALSE}
## Load package
library(rmiscfun)

## Check documentation
help("glance_data")

## Summarize iris dataset
glance_data(iris)

```

#### `glance_data_in_workbook`


```{r glance_data_in_worksheet, eval = FALSE}
## Load package
library(rmiscfun)

## Check documentation
help("glance_data_in_workbook")

## Summarize iris dataset
glance_data_in_workbook(iris)

## Uncomment the following line to summarize iris dataset AND create Excel Worksheet
## glance_data_in_workbook(iris, "iris_in_excel.xlsx")


```


#### `plot_numerical_vars`

```{r plot_numerical_vars, eval = FALSE}
## Load package
library(rmiscfun)

## Check documentation
help("plot_numerical_vars")

plot_numerical_vars(iris, "pairwise")
plot_numerical_vars(iris, "density")
plot_numerical_vars(iris, "boxplot")
plot_numerical_vars(iris, "violin")
plot_numerical_vars(iris, "histogram")
plot_numerical_vars(iris, "qqplot")

```


#### `clean_colnames`

```{r clean_colnames, eval = FALSE}
## Load package
library(rmiscfun)

## Check documentation
help("clean_colnames")

input <- c("bart Simpson", "LisaSimpson", "maggie..simpson!",
                 "MARGE-Simpson", "Homer Simpson :-)")
clean_colnames(input)

```

#### `clean_col_content`

```{r clean_col_content, eval = FALSE}
library(rmiscfun)

clean_col_content(c("bart Simpson", "LisaSimpson",
                    "maggie..simpson!",
                    "MARGE-Simpson", "Homer Simpson :-)"))

## Get warning for factors.
clean_col_content(
  factor(c("bart  Simpson", "LisaSimpson",
           "maggie..simpson!", "MARGE-Simpson",
           "bart  Simpson", "Homer Simpson :-)"))
)
```
