---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# rmiscfun

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/gbasulto/rmiscfun.svg?branch=master)](https://travis-ci.org/gbasulto/rmiscfun)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/gbasulto/rmiscfun?branch=master&svg=true)](https://ci.appveyor.com/project/gbasulto/rmiscfun)
[![Codecov test coverage](https://codecov.io/gh/gbasulto/rmiscfun/branch/master/graph/badge.svg)](https://codecov.io/gh/gbasulto/rmiscfun?branch=master)
<!-- badges: end -->


The goal of rmiscfun is provide call functions that I use in different projects (at work and personal ones.)


## Prerequisites


1. Install [Rtools](https://cran.r-project.org/bin/windows/Rtools/) (Only if you are on Windows): Download and execute the recommended EXE file in [this link](https://cran.r-project.org/bin/windows/Rtools/).
1. Install `devtools` package in `R`:

``` r
install.packages("devtools")
```

## Installation

You can install the current version of rmiscfun from [GitHub](https://github.com/) with:

``` r
devtools::install_github("gbasulto/rmiscfun")
```

## Available Functions

| Function | Brief description |
| :-------------------- | :------------------------------------------------------------|
| `glance_data`         | Summarize both, categorical and numerical variables in a dataframe |
| `glance_data_in_worksheet` | Similar to `glance_data`, but it breaks the summary into types and allows the used to save it in an Excel Worksheet |


## Examples

#### `glance_data`


```{r glance_data, eval = FALSE}
## Load package
library(rmiscfun)

## Check documentation
help("glance_data")

## Summarize iris dataset
glance_data(iris)

```

#### `glance_data_in_worksheet`


```{r glance_data_in_worksheet, eval = FALSE}
## Load package
library(rmiscfun)

## Check documentation
help("glance_data_in_worksheet")

## Summarize iris dataset
glance_data_in_worksheet(iris)

## Uncomment the following line to summarize iris dataset AND create Excel Worksheet
## glance_data_in_worksheet(iris, "iris_in_excel.xlsx")


```

