---
title: "Interpolate Values"
author: "Guillermo Basulto-Elias"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Interpolate Values}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

<!-- Load packages suppressing messages -->

```{r, echo = FALSE}
suppressPackageStartupMessages(library(rmiscfun))
```

## Description

The function `interpolate_values` interpolates values with respect to another ordered variable. It returns a vector.

Suppose that you have have recorded a variable, say `myvar`, each three seconds. However, you want the values every two seconds. Assume that `myvar` is smooth (if numerical) or does it usually remains on the same value for several measurements, then `interpolate_values` will interpolate the values for you.

The parameter `direction` is set by default to `"down"`. It might also be equal to `"up"`. This is because the function combines the values of the two values of time (`t_out`, `t_in`) and uses `tidyr::fill()` to interpolate the values. The parameter `direction` is `.direction` in the latter function.

## Simple example

```{r setup}
library(rmiscfun)

df <- data.frame(t = c(1, 3, 7), vals = c("a", "b", "a"))

df

new_t <- c(1, 2, 4, 5)
new_vals <- with(df, interpolate_values(new_t, t, vals))

data.frame(new_t, new_vals)
```

## 
